Universal Anonymous Signatures

### 2022-09-20 prism-backend/research/gsac/formal-uas.tex
Forgot to update theorems. Need to sync with proofs.

In more detail, issuance unforgeability captures that all the credentials issued
by an honest issuer meet the requirements set by the corresponding issuance
function. Moreover, any credential used to support the request needs to belong
to a known user. Without conventional opening, we need to resort to extraction.
The adversary is required to output a credential identifier that must correspond
to an existing credential issuance interaction -- note that the transcript must
be available to us if it exists, as the issuer is honest. From this transcript,
we extract the witness used to compute the issuance function, which includes the
output of the issuance function claimed by the requestor, and the credential
identifiers of any used credential. The adversary wins if applying the output of
the issuance function applied to the extracted witness is not consistent, or if
the credential identifiers do not belong all to the same (known) user.

Signature unforgeability is simply a combination of known requirements in AC and
GS schemes. Namely, the adversary is required to output a valid signature, and
wins if the signature: (1) opens to a wrong value, or to a value that cannot be
processed by \Judge; (2), is not consistent with the expected $\Yeval =
(\yeval^0,\yeval^1)$ value; or (3), cannot be associated to known credentials
owned by a known user.

The respective properties, \ExpForgeIssue and \ExpForgeSign, are formally
defined in \figref{fig:exp-uas-unfor}).

@@

% \begin{theorem}[Issuance unforgeability of \CUASGen]
%   \label{thm:issue-forge-uas}
%   If the underlying NIZK used for \RelIss is zero-knowledge,
%   simulation extractable and sound, then our \CUASGen construction satisfies
%   issuance unforgeability as defined in \defref{def:issue-forge-uas}.
% \end{theorem}

% \begin{theorem}[Signing unforgeability of \CUASGen]
%   \label{thm:sign-forge-uas}
%   If the underlying NIZK scheme for \RelSig is simulation
%   extractable, the scheme for \RelIns is complete, the public key
%   encryption algorithm is correct, and the \SBCM scheme is correct and one-more
%   unforgeable, then our \CUASGen construction satisfies signing unforgeability
%   as defined in \defref{def:sign-forge-uas}, except with negligible probability.
% \end{theorem}

\begin{theorem}[Unforgeability of \CUASGen]
  \label{thm:forge-uas}
  If the underlying NIZK system for \RelSig is simulation extractable, the NIZK
  system for \RelIns is complete, the public key encryption algorithm is
  correct, and the \SBCM scheme is correct and one-more unforgeable, then our
  \CUASGen construction satisfies unforgeability as defined in
  \defref{def:forge-uas}, except with negligible probability.
\end{theorem}

>>>>

In more detail, issuance unforgeability captures that all the credentials issued
by an honest issuer meet the requirements set by the corresponding issuance
function. Moreover, any credential used to support a request needs to belong
to a known user. 
The adversary is required to output a credential identifier that must correspond
to an existing credential issuance interaction -- note that the transcript must
be available to us if it exists, as the issuer is honest. From this transcript,
we extract the witness used to compute the issuance function, which includes the
output of the issuance function claimed by the requestor, and the credential
identifiers of any used credential. The adversary wins if applying the output of
the issuance function applied to the extracted witness is not consistent, or if
the credential identifiers do not belong all to the same (known) user.

Signature unforgeability is a combination of known requirements in AC and
GS schemes. Namely, the adversary is required to output a valid signature, and
wins if the signature: (1) opens to a wrong value, or to a value that cannot be
processed by \Judge; (2), is not consistent with the expected $\Yeval =
(\yeval^0,\yeval^1)$ value; or (3), cannot be associated to credentials
owned by a known user.

We formalize the respective properties, \ExpForgeIssue and \ExpForgeSign, in
\figref{fig:exp-uas-unfor}.

@@

\begin{theorem}[Issuance unforgeability of \CUASGen]
  \label{thm:issue-forge-uas}
  \todo{Update}
  If the underlying NIZK used for \RelIss is zero-knowledge,
  simulation extractable and sound, then our \CUASGen construction satisfies
  issuance unforgeability as defined in \defref{def:issue-forge-uas}.
\end{theorem}

\begin{theorem}[Signing unforgeability of \CUASGen]
  \label{thm:sign-forge-uas}
  \todo{Update}
  If the underlying NIZK scheme for \RelSig is simulation
  extractable, the scheme for \RelIns is complete, the public key
  encryption algorithm is correct, and the \SBCM scheme is correct and one-more
  unforgeable, then our \CUASGen construction satisfies signing unforgeability
  as defined in \defref{def:sign-forge-uas}, except with negligible probability.
\end{theorem}

% \begin{theorem}[Unforgeability of \CUASGen]
%   \label{thm:forge-uas}
%   If the underlying NIZK system for \RelSig is simulation extractable, the NIZK
%   system for \RelIns is complete, the public key encryption algorithm is
%   correct, and the \SBCM scheme is correct and one-more unforgeable, then our
%   \CUASGen construction satisfies unforgeability as defined in
%   \defref{def:forge-uas}, except with negligible probability.
% \end{theorem}
